Rapid Cycleway Prioritisation Tool

### 2020-06-10 report.Rmd
PDF version

---
title: "Rapid Cycleway Prioritisation Tool"
subtitle: "Technical specification"
author: Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds
output: bookdown::word_document2
# output:
#   bookdown::pdf_document2:
#     toc: true
#     toc_depth: 1
bibliography:
 - refs.bib
 - report-refs.bib
 - code/index.bib
---

@@

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
```

@@

```{r rank, fig.cap="Illustration of the tabular output of the Rapid Cycleway Prioritisation Tool for West Yorkshire."}
knitr::include_graphics("figures/Screenshot_2020-06-09 West Yorkshire.png")
```

>>>>

---
title: "Rapid Cycleway Prioritisation Tool"
subtitle: "Technical specification"
author: Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds
# output: bookdown::word_document2
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 1
bibliography:
 - refs.bib
 - report-refs.bib
 - code/index.bib
---

@@

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", out.width = "100%")
```

@@

```{r rank, fig.cap="Illustration of the tabular output of the Rapid Cycleway Prioritisation Tool for West Yorkshire."}
knitr::include_graphics("figures/wyca.png")
```
